Identification of protoneutron star g-modes in gravitational-wave data \pcd{[PCD: alt. title]Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.}

### 2020-09-11 methods.tex
fixing ref

\begin{equation}
\label{model1}
r_i=\beta_1 f_i + \beta_2 f_i^2 +\beta_3 f_i^3 + \epsilon_i
\end{equation}
where $\epsilon_i$ are assumed to be independent zero-mean Gaussian errors with
variances $\sigma_i^2$ that increase with frequency $f_i$. The model for frequency-dependent
variances is
\begin{equation}
\log \sigma_i=\alpha_0+ \alpha_1 f_i + \alpha_2 f_i^2 + \delta_i
\end{equation}
with independent and identically zero-mean Gaussian errors $\delta_i$. The R-package \texttt{lmvar}
\cite{lmvar:2019} that implements a maximum likelihood approach was used to fit the model.

The best fitting model amongst polynomials of degree 1, 2, and 3  was chosen according to
the Aikaike information criterion with coefficients given in Table \ref{tab:model}, which is actually the model defined in \eqref{model1}.  The data and fit of the model including 95\% confidence bands are displayed in
Figure~\ref{fig:LMVAR}.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolating $f(t)$
for values in between the $t_i$. We then use equation (\eqref{model1}) to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An exemple is given in Figure \ref{fig:ratio} where the red points are the point estimates and
the grey bands represent 95\% confidence bands. Ratio values
computed using the mass and radius values obtained from the simulation code are shown in black.

>>>>

\begin{equation}
\label{eq:model1}
r_i=\beta_1 f_i + \beta_2 f_i^2 +\beta_3 f_i^3 + \epsilon_i
\end{equation}
where $\epsilon_i$ are assumed to be independent zero-mean Gaussian errors with
variances $\sigma_i^2$ that increase with frequency $f_i$. The model for frequency-dependent
variances is
\begin{equation}
\log \sigma_i=\alpha_0+ \alpha_1 f_i + \alpha_2 f_i^2 + \delta_i
\end{equation}
with independent and identically zero-mean Gaussian errors $\delta_i$. The R-package \texttt{lmvar}
\cite{lmvar:2019} that implements a maximum likelihood approach was used to fit the model.

The best fitting model amongst polynomials of degree 1, 2, and 3  was chosen according to
the Aikaike information criterion with coefficients given in Table \ref{tab:model}, which is actually the model defined in \eqref{eq:model1}.  The data and fit of the model including 95\% confidence bands are displayed in
Figure~\ref{fig:LMVAR}.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolating $f(t)$
for values in between the $t_i$. We then use equation \eqref{eq:model1} to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An exemple is given in Figure \ref{fig:ratio} where the red points are the point estimates and
the grey bands represent 95\% confidence bands. Ratio values
computed using the mass and radius values obtained from the simulation code are shown in black.
